Inference methods comparison for the simplified Naomi model using maximum mean discrepancy

### 2023-05-10 src/naomi-simple_mmd/mmd.Rmd
Update MMD report #42

```{r}
tmb <- readRDS("depends/tmb.rds")
aghq <- readRDS("depends/aghq.rds")
tmbstan <- readRDS("depends/tmbstan.rds")

depends <- yaml::read_yaml("orderly.yml")$depends
```

@@

```{r}
mmd1 <- kernlab::kmmd(matrix(tmb$fit$sample$beta_rho), matrix(tmbstan$mcmc$sample$beta_rho))
mmd2 <- kernlab::kmmd(matrix(aghq$quad$sample$beta_rho), matrix(tmbstan$mcmc$sample$beta_rho))

mmd1
mmd2
```

>>>>

```{r}
tmb <- readRDS("depends/tmb.rds")
aghq <- readRDS("depends/aghq.rds")
tmbstan <- readRDS("depends/tmbstan.rds")
```

@@

```{r}
par_samp_matrix <- function(sample) {
  x <- sample[!(stringr::str_ends(names(sample), "_out") | stringr::str_ends(names(sample), "_ll"))]
  do.call(rbind, x)
}

tmb_samples <- par_samp_matrix(tmb$fit$sample)
aghq_samples <- par_samp_matrix(aghq$quad$sample)
tmbstan_samples <- par_samp_matrix(tmbstan$mcmc$sample)

#' Keep only the final 1000 samples from tmbstan
tmbstan_samples <- tmbstan_samples[, 4001:5000]

mmd_tmb <- kernlab::kmmd(tmb_samples, tmbstan_samples, kernel = "rbfdot")
mmd_aghq <- kernlab::kmmd(aghq_samples, tmbstan_samples, kernel = "rbfdot")

#' Take sigma to be the mean estimated for the two different methods
kpar <- list(sigma = mean(mmd_tmb@kernelf@kpar$sigma, mmd_aghq@kernelf@kpar$sigma))

#' Rerun with sigma the same across the different tests
mmd_tmb <- kernlab::kmmd(tmb_samples, tmbstan_samples, kernel = "rbfdot", kpar = kpar, alpha = 0.05)
mmd_aghq <- kernlab::kmmd(aghq_samples, tmbstan_samples, kernel = "rbfdot", kpar = kpar, alpha = 0.05)

mmd_tmb
mmd_aghq

mmd_tmb@mmdstats
mmd_aghq@mmdstats

round(100 * (mmd_aghq@mmdstats[1] - mmd_tmb@mmdstats[1]) / mmd_tmb@mmdstats[1])
round(100 * (mmd_aghq@mmdstats[2] - mmd_tmb@mmdstats[2]) / mmd_tmb@mmdstats[2])
```
